\documentclass{resume}

\usepackage[left=0.75in,top=0.6in,right=0.75in,bottom=0.6in]{geometry}

\name{Joydeep Bhattacharjee}
\address{ Senior Applied AI Researcher  }
\address{ +91~$\cdot$~8981849869 \\ joydeepubuntu@gmail.com \\ Bengaluru  }


\def\nameskip{\bigskip}
\def\sectionskip{\medskip}

\begin{document}

  Highly skilled Senior Machine Learning Staff Engineer with 13+ years of experience and expertise in LLMs, Deep Learning, AI applications, and NLP, demonstrating a proven track record of driving innovation in semiconductor and conversational AI domains. Expertise spans research, development, and implementation of cutting-edge machine learning solutions across manufacturing and technology sectors. Published two books in machine learning.

  \begin{rSection}{Technical Strengths}
    \begin{tabular}{ @{} >{\bfseries}l @{\hspace{6ex}} l }
      Data Science : & LLM, Deep Learning, Machine Learning, \\ & Natural Language Processing, Statistics, Algebra \\
      Computer Languages and packages : & Python, Tensorflow, Pytorch, Flask \\
      Databases : & MySQL, PostgreSQL, Elastic Search, MongoDB \\
      Cloud : & AWS, Azure, GCP
    \end{tabular}
  \end{rSection}
  
  \begin{rSection}{Experience}

    \begin{rSubsection}{Samsung Semiconductor India Research}{Jul 2022 - present}{Senior Machine Learning Staff Engineer - python, tensorflow, pytorch, RAG/LLM/NLP}{Bengaluru, India}
    \item Research and implementation of novel Retrieval Augmented Generation (RAG) + LLM application for breakdown maintenance of semiconductor manufacturing equipment. Implement and integrate RAG-based LLM models into production environments. In current application, brought down the mean response time from 30 seconds to less than 10 seconds by 70\%.
    \item Applied Research in the area of Deep Learning and its application in semiconductor manufacturing processes. Responsible for improving FAB yield using Deep Learning and AI models. Work on original research. As part of project performed more than 100 experiments in 2025.
    \item Handle large datasets and develop data pipelines to provide inputs for training and testing models.
    \item Lead and mentor a team of AI researchers, define technical roadmap and architecture for AI projects.
    \item Collaborate with cross-functional teams, including product managers, and front-end developers, to design solutions that meet business goals.
    \end{rSubsection}
  
    \begin{rSubsection}{yellow.ai}{Jan 2021 - Jul 2022}{Engineering Manager (NLP) - python, tensorflow, pytorch, keras, NLP}{Bengaluru, India}
    \item Design and implement next generation AI/NLP infrastructure for building and deploying thousands of models at scale in conversational AI.
    \item Responsible for research, development, production, and scaling of full pipeline of message flow and other intelligent NLP systems in multi‐lingual and multi‐modal contexts.
    \item Research, implementation, benchmark existing literature for various purposes.
    \item Leading the team which works in parallel and in collaboration to produce custom‐made algorithms using machine learning/Deep learning frameworks‐libraries like torch/hugging face/TensorFlow.
    \item Prepare production‐ready code with pre/postprocessing and native scaling in Kubernetes or on‐prem environment.
    \item Lead MLOps Initiatives and Cloud infra management for ML‐related service. Scaled up inference pipeline from 4 million messages per day to 10 million messages per day within 1 year.
    \item As a lead, I was answerable for client issues (explanation on models prediction and performance), custom requirements, new product feature exploration, POCs, architecture and design discussion, problem solving, hiring, mentorship and other decision making tasks.
    \end{rSubsection}
  
    \begin{rSubsection}{Nineleaps Technology Solutions}{May 2017 - Dec 2020}{Technical Lead - Data Science, Spark, Scikit-learn}{Bengaluru, India}
    \item Worked on projects such as Retail Demand Forecasting and Medical Analytics Application
    \item Design ML and Optimization architectures for Inventory Forecasting and Optimization system for 40000 products across thousands of stores
    \item Deployment and maintenance of highly available forecasting application.
    \item Built the model deployment lifecycle from ground up: model versioning, deployment, monitoring and dashboarding.
    \item Public health knowledge graph. Built ETL pipelines, data‐access and querying layer for graph DB at a scale of 1B+ edges and 200M+ nodes.
    \end{rSubsection}

    \begin{rSubsection}{Previous Experience}{2011-2017}{Python Developer}{Bengaluru \& Kolkata}
    \item HackerEarth - Category Head - Python - Nov 2016 - May 2017
    \item SLK Software Services Private Ltd. - Software Engineer - Aug 2015 - Oct 2016
    \item Tata Consultancy Services - Systems Engineer - Dec 2011 - Jul 2015
    \end{rSubsection}
  
  \end{rSection}
  
  \begin{rSection}{Education}
    {\bf National Institute of Technology, Silchar} \hfill {\em July 2011} \\ 
    { B.Tech in Electrical Engineering } \\
    Overall GPA: 6.98
  \end{rSection}
  
  \begin{rSection}{Publications}

    \begin{rSubsection}{Practical Machine Learning with Rust}{Dec 2019}{Book}{https://link.springer.com/book/10.1007/978-1-4842-5121-8}
    \item Explore machine learning in Rust and learn about the intricacies of creating machine learning applications. This book begins by covering the important concepts of machine learning such as supervised, unsupervised, and reinforcement learning, and the basics of Rust. Further, you’ll dive into the more specific fields of machine learning, such as computer vision and natural language processing, and look at the Rust libraries that help create applications for those domains. We will also look at how to deploy these applications either on site or over the cloud.
    \end{rSubsection}
    
    \begin{rSubsection}{fastText Quick Start Guide}{Jul 2018}{Book}{https://www.amazon.com/dp/1789130999}
    \item Facebook's fastText library handles text representation and classification, used for Natural Language Processing (NLP). Most organizations have to deal with enormous amounts of text data on a daily basis, and gaining efficient data insights requires powerful NLP tools such as fastText. This book is your ideal introduction to fastText.
    \end{rSubsection}
    
  \end{rSection}
  
  \begin{rSection}{Other Links}
    \begin{tabular}{ @{} >{\bfseries}l @{\hspace{6ex}} l }
      LinkedIn : & https://www.linkedin.com/in/joydeep-bhattacharjee-934a1157/ \\
      YouTube : & https://www.youtube.com/@joydeepbhattacharjee3849 \\
      Github : & https://github.com/infinite-Joy \\
      HuggingFace : & https://huggingface.co/infinitejoy
    \end{tabular}
  \end{rSection}

\end{document}
